Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-16 doc/manuscript/ESSDmanuscript.Rmd
Update ESSDmanuscript.Rmd

**The International Panel on Climate Change (IPCC) provides guidance for national greenhouse gas (GHG) inventories for reporting to the United Nations Framework Convention on Climate Change [UNFCCC, (REFS for older guidelines), @ipcc_2019_2019].**
Under this guidance, GHG inventories are to include all managed land, including most of the world's forest land [@ogle_delineating_2018].
The IPCC inventory guidelines include specific instructions for accounting for forest land ... [@ipcc_agriculture_2006; @ipcc_2019_2019a].
This guidance has improved as more of the relevant underlying data has become available [@requenasuarez_estimating_2019], but there remains room for continuous improvement as the science advances.
For example, @cook-patton_mapping_2020 *(summarize IPCC comparison results)*. 
*Moreover, it is useful for those compiling national greenhouse gas inventories to have access to locally-specific information, when available.*
To improve the data accessible for C accounting, the IPCC created the Emission Factor Database (EFDB; https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a recognized library of emission factors and other parameters that can be used for estimating greenhouse gas emissions and removals.

>>>>

**The International Panel on Climate Change (IPCC) provides guidance for national greenhouse gas (GHG) inventories for reporting to the United Nations Framework Convention on Climate Change [UNFCCC, (REFS for older guidelines), @ipcc_2019_2019].**
Under this guidance, GHG inventories include all managed land, including most of the world's forest land [@ogle_delineating_2018].
The IPCC inventory guidelines include specific instructions for accounting for forest land ... [@ipcc_agriculture_2006; @ipcc_2019_2019a].
This guidance has improved as more of the relevant underlying data has become available [@requenasuarez_estimating_2019], but there remains room for continuous improvement as the science advances.
For example, @cook-patton_mapping_2020 *(summarize IPCC comparison results)*. 
*Moreover, it is useful for those compiling national greenhouse gas inventories to have access to locally-specific information, when available.*
To improve the data accessible for C accounting, the IPCC created the Emission Factor Database (EFDB; https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a recognized library of emission factors and other parameters that can be used for estimating greenhouse gas emissions and removals.
